\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2018-08-07 paper/ms.tex
Contributors

\documentclass[article]{jss}
\usepackage{thumbpdf,lmodern} 
\graphicspath{{Figures/}}

@@

\section*{Acknowledgments}
John Veitch (Birmingham)
and Jorge Alarcon Ochoa (Rensselaer Polytechnic Institute)
provided helpful comments on an early
version of the manuscript.
It is a pleasure to thank Anna Pancoast (Harvard),
Ewan Cameron (Oxford), David Hogg (NYU), Daniela Huppenkothen (NYU),
and Iain Murray (Edinburgh)
for valuable discussions. This work was supported by a Marsden Fast-Start grant
from the Royal Society of New Zealand.

>>>>

\documentclass[article]{jss}
\usepackage{thumbpdf,lmodern} 
\usepackage[utf8]{inputenc}
\graphicspath{{Figures/}}

@@

\section*{Acknowledgments}
Other contributors to \pkg{DNest4} include
João Faria (Porto), Matt Pitkin (Glasgow), and Mat Varidel (Sydney).
John Veitch (Birmingham)
and Jorge Alarcon Ochoa (Rensselaer Polytechnic Institute)
provided helpful comments on an early
version of the manuscript.
It is a pleasure to thank Anna Pancoast (Harvard),
Ewan Cameron (Oxford), David Hogg (NYU), Daniela Huppenkothen (NYU),
and Iain Murray (Edinburgh)
for valuable discussions over the years.
This work was supported by a Marsden Fast-Start grant
from the Royal Society of New Zealand.
